
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Career Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
%---------------------------------------------------------

   %---------------------------------------------------------
   %	LAZ Parking
   %---------------------------------------------------------
   {\normalsize \textbf{LAZ Parking \hfill 03/2021 - Current}} \\
   {\sl Software Developer} \\

   % Work on E2
   % Build E2 Lite as a lightweight use of E2 for E2 Pods system.

   %---------------------------------------------------------
   %	INSURITY
   %---------------------------------------------------------
   {\normalsize \textbf{ INSURITY \hfill 06/2014 -- 03/2020}} \\
   {\sl Senior Software Developer} \\
   {\sl Previous Roles: Software Engineer \& Senior Software Engineer} \\

   \begin{itemize}
      \item As a member of a technology team supporting 13 Property \& Causality
         Lines of Business supporting Rating, Mapping, Statistical Coding, and Policy 
         Forms Generation:
         \begin{itemize}
            \item Delivered new functionality in alignment with business needs and 
               regulatory requirements.
            \item Remediated Defects for both Legacy and strategic product lines. 
            \item Modernized / Refactored codebase to increase maintainability \& 
               readability.
            \item Implemented technology to support new lines of business (Farm and Cargo).
         \end{itemize}

      \item As a liaison between the Policy and Billing system areas:
         \begin{itemize}
            \item Created XML code to enable information sharing between Policy Billing 
               systems.
            \item Standardized policies and procedures for the interaction between the 
               two systems.
         \end{itemize}

      \item Modernized error reporting, by designing and creating an automated system, 
         in PowerShell to increase visibility with email notification with categorization
         of errors.

      \item Developed interfaces to feed Reporting Systems, implementing new clients 
         and adding enhancements for current clients on these systems. In addition, 
         became the subject matter expert, providing training and assistance to 
         other team members.

      \item Spearheaded a project to upgrade the XML engine for legacy systems.
         \begin{itemize}
            \item Involved creating a development and testing environment for entire
               legacy system by utilizing an isolated build machine and test machines
               that existed outside the standard build and update system.
         \end{itemize}
   \end{itemize}

   \newpage

   %---------------------------------------------------------
   %	TRAVELERS
   %---------------------------------------------------------
   {\normalsize \textbf{ TRAVELERS \hfill 2011, 2012, 2013}} \\
   {\sl Technology Summer Intern for ICS (formerly known as OAI-SYS)} \\

   \begin{itemize}
      \item Advanced Technologies
         \begin{itemize}
            \item Created Perl 5 scripts to increase efficiency and automation.
            \item Fixed web applications to allow for cross-browser compatibility.
            \item Remotely reinstalled firewall device operation system and created 
               written documentation.
         \end{itemize}

      \item Service Management
         \begin{itemize}
            \item Created Perl 5 scripts to increase efficiency and automation of 
               Server Audits.
            \item Performed Server Audits.
            \item Headed XMatters add-on research to increase escalation efficiency.
            \item Worked on N05/C03 patches for BMC TM ART monitoring system.
         \end{itemize}

      \item Information - Systems Security
         \begin{itemize}
            \item Created Perl 5 scripts to perform metrics on compliance.
            \item Created and maintained database of Portable Media Exceptions.
            \item Created basic list of endpoint security.
         \end{itemize}

      \item[] \hspace{-0.4cm} Capstone Projects
         \begin{itemize}
            \item Research/Find Open-Source/FOSS solutions to replace current Proprietary
               software in current use at Travelers.
            \item Research/Find methods of Automation to increase efficiency at Travelers.
         \end{itemize}

   \end{itemize}

   %---------------------------------------------------------
\end{cvparagraph}
